---
title: "Trees"
author: "Mandy Langlois"
format: html
editor: visual
---

```{r}
library(tidyverse)
library(ggthemes)
library(lubridate)
```

```{r}
data= read_csv(here::here("RDS-2016-0005-2","Data", "TS3_Raw_tree_data.csv"))

```

```{r}
head(data)
```

# \[:alpha:\] - all alphabetic characters (A-Z, a-z, and locale-specific letters)

#  \[:lower:\] - lowercase letters

#  \[:upper:\] - uppercase letters

#  \[:digit:\] - digits 0-9

#  \[:space:\] - whitespace (spaces, tabs, etc.)

#  \[:alnum:\] - Alphabetic and numeric characters

#  \[:punct:\] - Punctuation

```{r}
city_state= str_match(data$City, "^([^,]+),[[:space:]]*([[:alpha:]]{2})$")
head(data)
```

```{r}
data[,c ("City","State")] = str_match(data$City, "^([^,]+),[[:space:]]*([[:alpha:]]{2})$")[,2:3]



head(data)

```

Determining how many records are in each State for Q1. This table is arranged in descending order to show the sate with the largest sample size.

```{r}
State_count = data |>
  group_by(State) |>
  summarize(record_count = n()) |>
  arrange(desc(record_count))

head(State_count)
```

```{r}
data_NC_SC = data |>
  filter(State == "NC" | State == "SC" )

  
```

```{r}
Cities = unique(data_NC_SC$City)
head(Cities)
  


```

```{r}
data_NC_SC = data_NC_SC |>
  mutate(Genus = str_extract(ScientificName, "^[[:alpha:]]+"))
```

```{r}
genus_avg <- data_NC_SC |>
  group_by(Genus) |>
  summarize(Average_Crown_Diameter = mean(`AvgCdia (m)`, na.rm = T)) |>
  arrange(desc(Average_Crown_Diameter))

largest_crown_genus = genus_avg |>
  head(1)

head(largest_crown_genus)
```

**Final Write up**

Q1. According to the table above CA has 4062 records, WA has 994 records, ID has 923 records, HI has 918 records, FL has 895, and IN has 877 records.

Q.2 They collected data from Charlotte,NC and Charleston, SC.

Q3. Quercus has the largest crown diameter in North and South Carolina with crown size of 13.6 (m).

|     |     |
|:----|----:|
|     |     |
